Adaptive Sequential Model Selection

### 2015-07-17 paper.tex
added guarantees to tables, diabetes example

\begin{table}[ht]
\centering
\begin{tabular}{rrrrr}
  \hline
  Method, Stopping rule& $p_{\text screen}$ & FWER$_{\text mod}$ & FDR$_{\text mod}$ &FDR$_{\text var}$ \\
% & \$p\_\{$\backslash$text\{screen\}\} & \$$\backslash$text\{FWER\}\_\{$\backslash$text\{model\}\}\$ & \$$\backslash$text\{FDR\}\_\{$\backslash$text\{model\}\}\$ & \$$\backslash$text\{FDR\}\_\{$\backslash$text\{variable\}\}\$ \\ 
  \hline
Nominal, Simple & 0.832 & 0.252 & 0.097 & 0.171 \\ 
  Nominal, Forward & 0.931 & 0.896 & 0.345 & 0.426 \\ 
  Nominal, Strong & 0.003 & 0.000 & 0.000 & 0.035 \\ 
  \hline
  MaxT, Simple & 0.369 & 0.000 & 0.002 & 0.042 \\ 
  MaxT, Forward & 0.668 & 0.038 & 0.026 & 0.080 \\ 
  MaxT, Strong & 0.025 & 0.006 & 0.004 & 0.038 \\ 
  \hline
  MaxT-Identify, Simple & 0.404 & 0.000 & 0.002 & 0.042 \\ 
  MaxT-Identify, Forward & 0.688 & 0.039 & 0.026 & 0.082 \\ 
  MaxT-Identify, Strong & 0.024 & 0.003 & 0.002 & 0.037 \\ 
  \hline
  Saturated, Simple & 0.000 & 0.000 & 0.000 & 0.029 \\ 
  Saturated, Forward & 0.013 & 0.001 & 0.000 & 0.030 \\ 
  Saturated, Strong & 0.000 & 0.000 & 0.000 & 0.033 \\ 
  \hline
  Knockoff & 0.252 &  &  & 0.103\\ 
  Knockoff+& ??   &  &    &   0.000? \\
   \hline
\end{tabular}
\caption[tab:stopping]{\em Results of various stopping rules applied to simulated data with 7 strong signals,  as described at the beginning of Section \ref{sec:sparseReg}.
The {\tt Simple} rule stops at the first time that a p-value exceeds $\alpha$, while {\tt Forward} and {\tt Strong} refers to the ForwardStop and StrongStrop rules of Section \ref{sec:sequential}.}
\label{tab:stopping}
\end{table}

>>>>

\begin{table}[ht]
\centering
\input{tables/error_rates_05.tex}
\caption[tab:stopping]{\em Results of various stopping rules applied to simulated data with 7 strong signals,  as described at the beginning of Section \ref{sec:sparseReg}.
The {\tt Simple} rule stops at the first time that a p-value exceeds $\alpha=0.05$, while {\tt Forward} and {\tt Strong} refers to the ForwardStop and StrongStrop rules of Section \ref{sec:sequential}. Results with theoretical guarantees are \guarantee{highlighted}.}
\label{tab:stopping05}
\end{table}

\begin{table}[ht]
\centering
\input{tables/error_rates_20.tex}
\caption[tab:stopping]{\em Results of various stopping rules applied to simulated data with 7 strong signals,  as described at the beginning of Section \ref{sec:sparseReg}.
The {\tt Simple} rule stops at the first time that a p-value exceeds $\alpha=0.2$, while {\tt Forward} and {\tt Strong} refers to the ForwardStop and StrongStrop rules of Section \ref{sec:sequential}. Results with theoretical guarantees are \guarantee{highlighted}.}
\label{tab:stopping20}
\end{table}
